---
author: "Benson Kenduiywo"
date: "2023-01-12"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60))
opts_knit$set(global.par = TRUE)
```

## Soil salinity 

### Donwload data

Download salinity data available from [Hassani et al. (2020)](https://doi.org/10.6084/m9.figshare.13295918.v1).

```{r d1}
root <- "D:/Data/HERplus/"
options(timeout=36000)
getSalinity <- function(url, path){
  temp <- tempfile()
  download.file(url,temp ,mode = "wb")
  unzip(temp, exdir = path)
}
if(!file.exists(paste0(root, "Salinity/"))){
  getSalinity("https://figshare.com/ndownloader/files/25617323", root)
  getSalinity("https://figshare.com/ndownloader/files/25616990", root)
  getSalinity("https://figshare.com/ndownloader/files/25617050", root)
  getSalinity("https://figshare.com/ndownloader/files/25617098", root)
}

```

### Administrative boundary

Get Bangladesh level 4 administrative boundaries.

```{r d2, warning=FALSE, message=FALSE}
library(raster)
shp <- getData("GADM",country="Bangladesh",level=4)
plot(shp)
```


### Spatial Metrics

Extract spatial salinity metrics by aggregating salinity in a given year in each admin 4 boundary.

```{r s1, warning=FALSE, message=FALSE}
filename <- paste0(root,"Salinity/Bangladesh_spatial_temporal_salinity.csv")

if(!file.exists(filename)){
  files <- list.files(paste0(root,"Salinity/"),pattern = (".tif$"), recursive = TRUE, full.names = TRUE)
  knitr::kable(head(files), caption = 'Salinity raster files')
  library(terra)
  shp <- vect(shp)
  df <- data.frame(Name4=shp$NAME_4)
  for(i in 1:length(files)){
    temp <- extract(rast(files[i]), shp, fun=mean, na.rm=TRUE, ID=F)
    df <- cbind(df, temp)
  }
  colnames(df)[-1] <- gsub("ECe_","",names(df)[-1])
  write.csv(df, filename)  
}                      


```


## CHIRPS DONWLOAD


## References

Hassani, Amirhossein; Azapagic, Adisa; Shokri, Nima (2020): Predicting Long-term Dynamics of Soil Salinity and Sodicity on a Global Scale. [*figshare*. Dataset](https://doi.org/10.6084/m9.figshare.13295918.v1).  

